An ultra-low noise, high-voltage piezo driver

### 2016-09-04 piezo.tex
(hopefully) final round of edits.

@@

\author{N.C. Pisenti}
\email[]{npisenti@umd.edu}
\author{A. Restelli}
\author{B.J. Reschovsky}
\author{D.S. Barker}
\author{G.K. Campbell}
\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology}

@@

\begin{abstract}
We present an ultra-low noise, high-voltage driver suited for use with piezoelectric actuators and other low-current applications. 
The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
A high slew-rate op-amp suppresses the residual switching noise, yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed with unity gain directly onto the output, making the driver well-suited for closed-loop feedback applications.
Digital control enables both repeatable setpoints and sophisticated control logic. 
The circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
\end{abstract}

@@

Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients.
In addition, the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}

Laboratory devices are often operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but  the input voltage is often gained such that it spans the entire output range of the device.
While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high-voltage output. 
Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.

We present a circuit with a hybrid architecture.
The high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications  (see Sec.~\ref{Sec:LowNoiseStabilization}).
This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
We present a noise analysis of our circuit in Sec.~\ref{Sec:NoiseAnalysis}, and show characteristic performance data in Sec.~\ref{Sec:Results}.
Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.\cite{PiezoDesignFiles}
The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits comfortably into a compact eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
%The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}

Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
To improve the large-amplitude slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to reduce the $RC$ time constant of the high-voltage node $\text{V}_\text{out}$ when needed.
A low-pass filter with a switchable corner frequency can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
This node is DC-coupled to the high-voltage output, and is useful for closed-loop feedback control.

@@

The high-voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver.\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
This integrated circuit can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
When the switch closes to ground, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
In this state, the output diode D1 is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
By changing the switching duty cycle, the DRV2700 is able to regulate the voltage across the galvanically isolated output (nodes $\text{V}_\text{FG}$ and $\text{V}_\text{HV}$ in Fig.~\ref{Fig:PiezoCircuit}).

The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal \SI{1.3}{\volt} reference.
The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
The op-amp U1 subtracts $\text{V}_\text{FG}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node $\text{V}_\text{HV}$, ensuring the DRV2700 regulates the output voltage such that
\begin{align}
\label{Eq:U1Output}
\text{V}_\text{HV} - \text{V}_{\text{FG}} &= G\cdot \text{V}_{\text{ctl}}\,,
\end{align}
where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$, and $\text{V}_\text{ctl}$ is the control voltage set by the DAC.
The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
\begin{align}
\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}\,,
\end{align}
as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output. 
A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet.\cite{DRV2700Datasheet,DRV2700EVMUserGuide}

The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a resonance in spectroscopy), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
Additional capacitors on both the $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$ resistor networks shunt high frequency noise to ground.
This filter topology, modeled on a lossy transmission line, is sufficient for our application, but other corner frequencies or topologies could also be used.

@@

The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated floating ground of the flyback converter; see U2 in Fig.~\ref{Fig:PiezoCircuit}.
This op-amp senses the voltage $\text{V}_\text{out}$ referenced to true circuit ground, and adjusts its output such that
\begin{align}
\text{V}_\text{out} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{ctl} -
\left(\frac{R_1}{R_\text{mod}}\right) \text{V}_\text{mod}\,.
\label{Eq:FullTransferFunc}
\end{align}
Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$ and is inverted before being summed onto the output.
We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
Depending on the application, other gain configurations could work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they both derive from $\text{V}_\text{ctl}$).

The output of U2 can be viewed in two ways.
At low frequencies, it modifies the floating ground reference $\text{V}_\text{FG}$ for the flyback converter, which regulates the voltage between $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$.
At higher frequencies, U2 is decoupled from $\text{V}_\text{FG}$ by the passive filtering network.
Instead, $\text{C}_\text{out}$ provides a low-impedance path directly to the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
A small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation, although smaller values might also work and provide better performance.
%
%
%
%Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to $\text{V}_\text{FG}$.
%Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
%At low frequencies, this amounts to changing the floating ground reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{out}$ provides a low-impedance pathway to $\text{V}_\text{out}$.
%Thus, U2 simultaneously suppresses residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.

@@

The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
This has two advantages: digital control enhances setpoint repeatability, and simplifies integration with a wide variety of computerized control electronics or more sophisticated servo loops.
While the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.

As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2.
This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
It consists of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with a secondary \SI{10}{\micro\farad} capacitor that can be switched in to operate with the lower corner frequency.

One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
If that voltage drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing $\text{C}_\text{out}$ to be quickly discharged.
The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.

@@

Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated push button.
The encoder/push button provide menu navigation, and the switch toggles between DC and scanning operation.
However, other user interfaces can easily be designed to work with the existing hardware.
Arduino-based code\cite{Arduino} written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.

The circuit fits into a standard Eurocard module (3U by 12HP by \SI{160}{\milli\meter}), and is mounted in a Eurocard rack to supply power at $\pm\SI{15}{\volt}$.
While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
This vastly expands the conceivable control scenarios. 
For example, in our lab we implement a slow-feedback lock of external-cavity diode lasers to a wavemeter.
Software on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
Other similar schemes are possible, enabling complete remote control of the laser electronics.

The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel or from the backplane.
This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
In either case, this voltage is differentially buffered to break ground loops.
An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller.\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor. Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation. This will be a very useful feature to prevent the servo controller from railing.}
The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
The high-voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
Further details on the design features discussed in this section, including sample software, can be found on Github.\cite{PiezoDesignFiles}

@@

The authors would like to thank Z. Smith for useful discussions.
This work was partially supported by the Office of Naval Research, and the National Science Foundation through the Physics Frontier Center at the Joint Quantum Institute.

>>>>

\usepackage{natbib}

@@

\author{N.C. Pisenti}
\email[]{npisenti@umd.edu}
\author{A. Restelli}
\author{B.J. Reschovsky}
\author{D.S. Barker}
\author{G.K. Campbell}
\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology \\ College Park, MD 20742, USA}

@@

\begin{abstract}
We present an ultra-low noise, high-voltage driver suited for use with piezoelectric actuators and other low-current applications. 
The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
A high slew-rate op-amp suppresses the residual switching noise, yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed with unity gain directly onto the output, making the driver well-suited for closed-loop feedback applications.
Digital control enables both repeatable setpoints and sophisticated control logic, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
\end{abstract}

@@

Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}

Laboratory devices are often operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but  the input voltage is often gained such that it spans the entire output range of the device.
While this has certain advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output. 
Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.

We present a circuit with a hybrid architecture.
The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
The schematic is presented in Sec.~\ref{Sec:Circuit}, with a noise analysis in Sec.~\ref{Sec:NoiseAnalysis} and characteristic performance data in Sec.~\ref{Sec:Results}.
Complete design files, including the schematic, bill of materials, and board layout, can be found on GitHub.\cite{PiezoDesignFiles}
The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.

Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
To improve the large-amplitude slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to reduce the $RC$ time constant of the high-voltage node $\text{V}_\text{out}$ when needed.
A low-pass filter with a switchable corner frequency can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
This node is DC-coupled to the high-voltage output, and is useful for closed-loop feedback control.

@@

The high-voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver.\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
This integrated circuit can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
In this state, the output diode D1 is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
By changing the switching duty cycle, the DRV2700 is able to regulate the voltage across the galvanically isolated output (nodes $\text{V}_\text{FG}$ and $\text{V}_\text{HV}$ in Fig.~\ref{Fig:PiezoCircuit}).

The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal \SI{1.3}{\volt} reference.
The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
The op-amp U1 subtracts $\text{V}_\text{FG}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node $\text{V}_\text{HV}$, ensuring the DRV2700 regulates the output voltage such that
\begin{align}
\label{Eq:U1Output}
\text{V}_\text{HV} - \text{V}_{\text{FG}} &= G\cdot \text{V}_{\text{ctl}}\,,
\end{align}
where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$, and $\text{V}_\text{ctl}$ is the control voltage set by the DAC.
The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
\begin{align}
\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}\,,
\end{align}
as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
In our implementation, we choose a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output. 
A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet.\cite{DRV2700Datasheet,DRV2700EVMUserGuide}

The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
The corner frequency $f_c \approx \SI{30}{\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a resonance in spectroscopy), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
Additional capacitors on both the $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$ resistor networks shunt high frequency noise to ground.
This filter topology, modeled on a lossy transmission line, is sufficient for our application, but other corner frequencies or topologies could also be used.

@@

The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}; see U2 in Fig.~\ref{Fig:PiezoCircuit}) drives the galvanically isolated floating ground of the flyback converter.
This op-amp senses the voltage $\text{V}_\text{out}$ referenced to true circuit ground, and adjusts its output such that
\begin{align}
\text{V}_\text{out} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{ctl} -
\left(\frac{R_1}{R_\text{mod}}\right) \text{V}_\text{mod}\,.
\label{Eq:FullTransferFunc}
\end{align}
Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$ and is inverted before being summed onto the output.
We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{ctl}$ is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
Depending on the application, other gain configurations could work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they both derive from $\text{V}_\text{ctl}$).

The op-amp U2 controls $\text{V}_\text{out}$ via two different feedback pathways.
At low frequencies, it modifies the floating ground reference $\text{V}_\text{FG}$ of the flyback converter, and the DRV2700 in turn modifies $\text{V}_\text{HV}$ to maintain a constant voltage between $\text{V}_\text{FG}$ and $V_\text{HV}$.
At higher frequencies, U2 is decoupled from $\text{V}_\text{FG}$ by the passive filtering network.
In this regime, $\text{C}_\text{out}$ provides a low-impedance path between U2 and the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
We settled on a value $\text{C}_\text{out}=\SI{1}{\micro\farad}$, which is a compromise between component size and the desire for a large capacitance.
In addition, a small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation.
Smaller $R_{11}$ and/or larger $\text{C}_\text{out}$ might provide better performance, but this has not been tested.

@@

The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
This has two advantages: digital control enhances setpoint repeatability, and simplifies the integration with computerized control electronics or sophisticated servo loops.
While the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.

As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
It consists of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with a secondary \SI{10}{\micro\farad} capacitor that can be switched in to operate with the lower corner frequency.

One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet\cite{DRV2700Datasheet}, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
If $\text{V}_\text{MG}$ drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing $\text{C}_\text{out}$ to be quickly discharged.
The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.

@@

Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated pushbutton.
The encoder/pushbutton provide menu navigation, and the switch toggles between DC and scanning operation.
However, other user interfaces can easily be designed to work with the existing hardware.
Arduino-based code\cite{Arduino} written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.

The circuit fits into a standard Eurocard module\footnote{Module size is 3U by 12HP by \SI{160}{\milli\meter}, see IEEE~Std~1101.11 for details.}, and is mounted in a Eurocard rack which supplies power at $\pm\SI{15}{\volt}$.
While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
This vastly expands the conceivable control scenarios. 
For example, in our lab we implement a slow-feedback lock of external-cavity diode lasers to a wavemeter.
Software on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
Other similar schemes are possible, enabling complete remote control of the laser electronics.

The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel or from the backplane.
This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
In either case, this voltage is differentially buffered to break ground loops.
An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller.\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor. Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation. This will be a very useful feature to prevent the servo controller from railing.}
The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
The high-voltage output can be interlocked with another signal on the backplane, permitting easy integration with existing laboratory interlock schemes if desired.
Further details on the design features discussed in this section, including sample software, can be found on GitHub.\cite{PiezoDesignFiles}

@@

\begin{acknowledgments}
The authors would like to thank Z. Smith for useful discussions.
This work was partially supported by the Office of Naval Research, and the National Science Foundation through the Physics Frontier Center at the Joint Quantum Institute.
\end{acknowledgments}

% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
\bibliography{references}

\end{document}
